---
title: "Code chunks"
author: "Stefano"
affiliation: "University of Trieste"
format:
  html:
    code-tools:     # used to show the code of the document in the html-rendered page
     source: true
     toggle: false
     caption: Show the code for this document
    toc: true
    toc-location: right
    grid:
      sidebar-width: 200px
      body-width: 900px
      margin-width: 400px
      gutter-width: 1.5rem
    theme:
      light: minty
      dark: superhero
number-sections: true
self-contained: true
lang: en
execute: 
  echo: false # this specifies the default behaviour of echo; you can still specify "echo: true" in a specific chunk
  warning: false
---

## Add a code chunk

For flow charts Mermaid is great but ask help to chatbots..

Now we add a code chunk below:

```{r}
head(cars)
```

To prevent the code from being shown but still make it run:
```{r}
#| echo: false
head(cars)
```

To show code without executing it:
```{r}
#| echo: true
#| eval: false
head(cars)
```

```{r}
#| lst-label: lst-default
#| lst-cap: Default settings
head(cars)
```

@lst-default presents the default settings of the code chunks

```{r}
# normal distribution plotting:
x <- seq(-3, 3, length.out = 1000)
plot(x, dnorm(x), type = "l", cex = 2, lwd = 3)
```

Then I can have a crossreference for the graph: @fig-normal presents a normal distribution
```{r}
#| label: fig-normal
#| fig-cap: A normal distribution
#| 
# normal distribution plotting:
plot(x, dnorm(x), type = "l", cex = 2, lwd = 3)
```

Then I can arrange plots in a figure:

```{r}
#| error: true
#| layout-ncol: 1
#| label: fig-normalProperties
#| fig-cap: Normal Distribution
#| fig-subcap:
#|   - "Density"
#|   - "Cumulative"
#|   - "Quantile"
x <- seq(-3,3, length.out= 1000)
plot(x, dnorm(x), type = "l", cex = 2, lwd = 3)
plot(x, pnorm(x), type = "l", cex = 2, lwd = 3)
plot(x, qnorm(x), type = "l", cex = 2, lwd = 3, xlim = c(0,1))
```

The error call can show/not-show errors for the code chunk. Same for warning call.

### Now we use knitr library to create a table. Kable function can be used to style it.

@tbl-mtcars is a table of a dataset. 
```{r}
library(knitr)
#| tbl-cap: My table
#| label: tbl-mtcars
kable(head(cars))
```



